---
title: "Dynamic models of interaction betadiversity"
output:
html_document:
  toc: true
  number_sections: true
  theme: spacelab
  keep_md: true
editor_options: 
chunk_output_type: console
---

```{r,warning=FALSE,message=FALSE,echo=FALSE,cache=FALSE}
library(chron)
library(dplyr)
library(ggplot2)
library(reshape2)
library(knitr)
library(R2jags)
library(dplyr)
library(stringr)
library(gridExtra)
library(boot)
library(foreach)
library(bipartite)
library(tidyr)
library(doSNOW)

opts_chunk$set(message=FALSE,warning=FALSE,fig.width=10,fig.height=7,echo=F,cache=F,fig.align='center',fig.path="figureObserved/")

#source functions
source("models/Functions.R")

newModel<-T
```

```{r,echo=F,cache=FALSE}
paste("Run Completed at",Sys.time())
```

```{r}
#reload if needed
#load("ObservedModel.RData")
```

#Load in data

```{r}
#read in flower morphology data, comes from Nectar.R
fl.morph<-read.csv("data/FlowerMorphology.csv")

#use effective corolla where possible.
fl.morph$Corolla<-fl.morph$EffectiveCorolla

fl.morph[is.na(fl.morph$Corolla),"Corolla"]<-fl.morph[is.na(fl.morph$Corolla),"TotalCorolla"]

#First row is empty
fl.morph<-fl.morph[-1,]

#Bring in Hummingbird Morphology Dataset, comes from
hum.morph<-read.csv("data/HummingbirdMorphology.csv")

#taxonomy change, we are calling them Crowned Woodnymph's now.
hum.morph$English<-as.character(hum.morph$English)

hum.morph$English[hum.morph$English %in% "Green-crowned Woodnymph"]<-"Crowned Woodnymph"

#Bring in Interaction Matrix
int<-read.csv("data/HummingbirdInteractions.csv")

int$timestamp<-as.POSIXct(paste(int$Time,int$DateP),format="%H:%M:%S %Y-%m-%d")

#one date error
int[int$DateP %in% '2013-07-25',"Month"]<-7

#one duplicate camera error, perhaps two GPS records.
int<-int[!(int$ID %in% "FH1108" & int$Date_F %in% '2014-12-01'),]

#Correct known taxonomic disagreements, atleast compared to traits
int[int$Iplant_Double %in% "Onagaraceae fuschia","Iplant_Double"]<-"Fuchsia macrostigma"
int[int$Iplant_Double=="Alloplectus purpureus","Iplant_Double"]<-"Glossoloma purpureum"
int[int$Iplant_Double=="Capanea affinis","Iplant_Double"]<-"Kohleria affinis"
int[int$Iplant_Double=="Columnea cinerea","Iplant_Double"]<-"Columnea mastersonii"
int[int$Iplant_Double=="Alloplectus teuscheri","Iplant_Double"]<-"Drymonia teuscheri"
int[int$Iplant_Double=="Drymonia collegarum","Iplant_Double"]<-"Alloplectus tetragonoides"

#Some reasonable level of presences, 4 points
keep<-names(which(table(int$Hummingbird) > 4))

#int<-int[int$Hummingbird %in% keep & !int$Hummingbird %in% c("Sparkling Violetear"),]

m.dat<-droplevels(int[colnames(int) %in% c("ID","Video","Time","Hummingbird","Sex","timestamp","TransectID","Transect_R","Iplant_Double","Pierce","DateP","Month","ele","Type")])

#Does the data come from camera or transect?
m.dat$Type<-(is.na(m.dat$TransectID))*1

m.dat$Year<-years(as.Date(m.dat$DateP))

#one missing date
m.dat$Year[m.dat$Year %in% 2012]<-2013
m.dat$Year[m.dat$Year %in% 2106]<-2016

#Number of bird species
h_species<-nlevels(m.dat$Hummingbird)

#Number of plant species
plant_species<-nlevels(m.dat$Iplant_Double)

#Get english name
dath<-merge(m.dat,hum.morph, by.x="Hummingbird",by.y="English",keep=all)

#Merge to flowers
int.FLlevels<-levels(factor(dath$Iplant_Double))

#Which flowers are we missing info for?
missingTraits<-int.FLlevels[!int.FLlevels %in% fl.morph$X]

#print(paste("Missing Trait Information:",missingTraits))
dath<-merge(dath,fl.morph, by.x="Iplant_Double",by.y="X")

#Drop piercing events, since they don't represent correlation
#dath<-dath[!dath$Pierce %in% c("y","Y"),]
```

##Match Species to Morphology

```{r}
#observed traitmatching
traitmatchF<-abs(t(sapply(hum.morph$Bill,function(x){x-fl.morph$Corolla})))
rownames(traitmatchF)<-hum.morph$English
colnames(traitmatchF)<-fl.morph$Group.1
```

```{r}
#match names #Round to 2 decimals #Convert to cm for winbugs, avoids numerical underflow
traitmatchT<-round(traitmatchF[rownames(traitmatchF) %in% dath$Hummingbird,colnames(traitmatchF) %in% dath$Iplant_Double],2)
traitmatchT<-traitmatchT[sort(rownames(traitmatchT)),sort(colnames(traitmatchT))]
```

##Elevation ranges

Create a binary variable whether each observation was in a low elevation or high elevation transect. We have some species that just occur at the top of the gradient, and are not present in the sampling window of flowers at the low elevation.

Accounting for non-availability.
We have to figure out which plants were sampled in which periods, and if it was sampled, the non-detection are 0 if it wasn't the non-detection are NA. then remove all the Na's.

```{r}
elevH<-read.csv("data/HummingbirdElevation.csv",row.names=1)
head(elevH)
colnames(elevH)[5]<-"Elevation"
elevH$Bird<-1:nrow(elevH)

#high elevation or low elevation
elevP<-read.csv("data/PlantElevation.csv",row.names=1)
colnames(elevP)[5]<-"Elevation"
elevP$Plant<-1:nrow(elevP)
elevP$Iplant_Double<-as.character(elevP$Iplant_Double)

#Merge to observed data
#plants
dathp<-merge(dath,elevP,by="Iplant_Double")

#birds
datph<-merge(dathp,elevH,by="Hummingbird")
```

What elevation transect is each observation in?
The camera data need to be inferred from the GPS point.

```{r}
#cut working best on data.frame
datph<-as.data.frame(datph)

#which elevation bin is each observation within
labs<-paste(seq(1300,2500,200),seq(1500,2700,200),sep="_")

#for the couple points that have 1290 elevation, round up to 300 for convienance
datph$ele[datph$ele < 1300]<-1301
datph$ele<-as.numeric(datph$ele)
datph$Transect_R[is.na(datph$Transect_R)]<-as.character(cut(datph[is.na(datph$Transect_R),]$ele,seq(1300,2700,200),labels=labs))

#Elev for the transects is the midpoint
tran_elev<-datph[datph$Survey_Type=='Transect',"Transect_R"]
datph[datph$Survey_Type=='Transect',"ele"]<-sapply(tran_elev,function(x){
mean(as.numeric(str_split(x,"_")[[1]]))
})
```

### Define Time Events

```{r}
#ID for NA is holger transects, make the id's 1:n for each day of transect at each elevation, assuming no elevation was split across days.
datph$ID<-as.character(datph$ID)
noid<-datph[is.na(datph$ID),]

id_topaste<-paste(noid$Month,noid$Year,"Transect",sep="_")
datph[which(is.na(datph$ID)),"ID"]<-id_topaste

#Create year month combination
datph$Time<-paste(datph$Month,datph$Year,sep="_")

#Label survey type
datph$Survey_Type<-NA

mt<-!is.na(datph$TransectID)*1
datph$Survey_Type[mt==1]<-"Transect"
datph$Survey_Type[!datph$Survey_Type %in% "Transect"]<-"Camera"

datph<-datph[datph$Survey_Type=="Camera",]

#time filter

#sort by timestamp
datph<-datph[order(datph$timestamp),]

dotime<-function(d){
d$Timediff<-NA
if(nrow(d)>1){
for (x in 2:nrow(d)){
d$Timediff[x]<-difftime(d$timestamp[x],d$timestamp[x-1],units="mins")  
}
}
return(d)
}

datph<-datph %>% group_by(ID,Hummingbird) %>% do(dotime(.))

#eliminate interaction by the same species within five minutes
datph<-datph[!1:nrow(datph) %in% which(datph$Timediff<5),]
#Day level
#add day ID
sdat<-split(datph,list(datph$ID),drop = T)

sdat<-lapply(sdat,function(x){
x<-droplevels(x)
x$Day<-as.numeric(as.factor(x$DateP))
return(x)
})

indatraw<-rbind_all(sdat)

#Species names
for (x in 1:nrow(indatraw)){
indatraw$Hummingbird[x]<-as.character(elevH[elevH$Bird %in% indatraw$Bird[x],"Hummingbird"])
indatraw$Iplant_Double[x]<-as.character(elevP[elevP$Plant %in% indatraw$Plant[x],"Iplant_Double"])
}

#match the traits
traitmelt<-melt(traitmatchT)
colnames(traitmelt)<-c("Hummingbird","Iplant_Double","Traitmatch")

#dummy presence variable
indatraw$Yobs<-1

#prune columns to make more readable
indatraw<-indatraw[,c("Hummingbird","Iplant_Double","ID","Time","Month","Year","Transect_R","ele","DateP","Yobs","Day","Survey_Type","Pierce")]

```

##Summarize daily interactions
To estimate the daily detectability, there can only be a max of one interaction per day.
We use mean elevation to average across observations within a transect

```{r}
indatraw<-indatraw %>% group_by(Hummingbird,Iplant_Double,ID,Day) %>% summarize(Yobs=sum(Yobs),Time=unique(Time),Transect_R=unique(Transect_R),Month=unique(Month),Year=unique(Year),ele=mean(ele),DateP=unique(DateP),Survey_Type=unique(Survey_Type)) %>% ungroup()
```

#Static betadiversity
```{r}

```

```{r}
indat<-prepData(indatraw)
```

#Modeling Fitting

```{r}
models<-list()
chains<-list()
networks<-list()
```


## Species Identity

```{r}
#Cut into slices
#Cut data into timeslices
indat<-indat %>% arrange(DateP)
indat$interval<-cut(as.POSIXct(indat$DateP),2)
indat$jinterval<-as.numeric(indat$interval)
intervals<-unique(indat$jinterval)

#For species identity, there can't be any species interactions not in the prediction dataset.
obs_levels<-indat %>% filter(jinterval==1) %>% distinct(Hummingbird,Iplant_Double) %>% mutate(i=paste(Hummingbird,Iplant_Double,sep="_")) %>% .$i

predict_levels<-indat %>% filter(jinterval==2) %>% distinct(Hummingbird,Iplant_Double) %>% mutate(i=paste(Hummingbird,Iplant_Double,sep="_")) %>% .$i

missing<-predict_levels[!predict_levels %in% obs_levels]
species_dat<-indat %>% filter(!paste(Hummingbird,Iplant_Double,sep="_") %in% missing) %>% droplevels()

#if those missing interactions eliminate a species overall
#Easiest to work with jags as numeric ordinal values
species_dat$Hummingbird<-as.factor(species_dat$Hummingbird)
species_dat$Iplant_Double<-as.factor(species_dat$Iplant_Double)
species_dat$jBird<-as.numeric(species_dat$Hummingbird)
species_dat$jPlant<-as.numeric(species_dat$Iplant_Double)

jagsIndexBird<-data.frame(Hummingbird=levels(species_dat$Hummingbird),jBird=1:length(levels(species_dat$Hummingbird)))

jagsIndexPlants<-data.frame(Iplant_Double=levels(species_dat$Iplant_Double),jPlant=1:length(levels(species_dat$Iplant_Double)))

#Similiarly, the trait matrix needs to reflect this indexing.
jTraitmatch<-traitmatchT[rownames(traitmatchT) %in% unique(species_dat$Hummingbird),colnames(traitmatchT) %in% unique(species_dat$Iplant_Double)]

species_dat$Index<-1:nrow(species_dat)
species_dat<-droplevels(species_dat)

#Turn Time and ID into numeric indexes
species_dat$jTime<-as.numeric(as.factor(species_dat$Time))
species_dat$jID<-as.numeric(as.factor(species_dat$ID))

#Split data
Yobs_dat<-species_dat[species_dat$jinterval <= intervals[1],]
Ynew_dat<-species_dat[species_dat$jinterval > intervals[1],]
```

$$ Yobs_{i,j} \sim Bernoulli(\lambda_{i,j}) $$

## Predicted

```{r}
#Source model
source("models/SpeciesIdentity.R")

#print model
writeLines(readLines("models/SpeciesIdentity.R"))

#Run Model
runModel<-function(Yobs_dat,Ynew_dat){
  
  #Inits
  InitStage <- function(){
    Ynew_pred<-rep(1,Dat$Nnewdata)
    list(Ynew_pred=Ynew_pred)}
  
  #Parameters to track
  ParsStage <- c("alpha","Ynew_pred","fit","fitnew")
  
  #Jags Data
  Yobs<-(Yobs_dat$Yobs > 0)*1
  Ynew<-(Ynew_dat$Yobs> 0)*1
  
  Dat<-list(
    Yobs=Yobs,
    Birds=max(Yobs_dat$jBird),
    Bird=Yobs_dat$jBird,
    Plant=Yobs_dat$jPlant,
    Plants=max(Yobs_dat$jPlant),
    Nobs=length(Yobs),
    NewBird=Ynew_dat$jBird,
    NewPlant=Ynew_dat$jPlant,
    Ynew=Ynew,
    Nnewdata=length(Ynew))
  
  #MCMC options
    system.time(
      m2<-jags(data=Dat,parameters.to.save=ParsStage,inits=InitStage,model.file="models/SpeciesIdentity.jags",n.thin=1,n.iter=1000,n.burnin=900,n.chains=2,DIC=F)
    )
    return(m2)
}

models$Species$Predicted<-runModel(Yobs_dat=Yobs_dat,Ynew_dat=Ynew_dat)
```

```{r}
#Get Chains
getChains<-function(mod){
  
  pc<-reshape2::melt(mod$BUGSoutput$sims.array)
  colnames(pc)<-c("Draw","chain","par","value")
  
  #extract parameter name
  pc$parameter<-data.frame(str_match(pc$par,"(\\w+)"))[,-1]
  
  #Extract index
  splitpc<-split(pc,pc$parameter)
  
  #single index
  splitpc[c("alpha")]<-lapply(
    splitpc[c("alpha")],function(x){
    sv<-data.frame(str_match(x$par,"(\\w+)\\[(\\d+),(\\d+)]"))[,3:4]
    colnames(sv)<-c("jBird","jPlant")
    pc<-data.frame(x,sv)
    })
  
  splitpc[c("Ynew_pred")]<-lapply(
    splitpc[c("Ynew_pred")],function(x){
    sv<-data.frame(str_match(x$par,"(\\w+)\\[(\\d+)]"))[,3]
    pc<-data.frame(x,Index=sv)
    })
    
  chains<-bind_rows(splitpc)
return(chains)}
```

```{r}
chains$Species$Predicted<-getChains(models$Species$Predicted)
```

###Assess Convergence

```{r,cache=FALSE,fig.width=13,fig.height=20}
###Chains
#ggplot(chains$Species$Predicted[chains$Species$Predicted$parameter %in% c("alpha"),],aes(x=Draw,y=value,col=as.factor(chain))) + geom_line() + facet_wrap(jPlant~jBird,scale="free") + theme_bw() + labs(col="Chain") 
```

```{r,fig.height=5}
ggplot(chains$Species$Predicted[chains$Species$Predicted$parameter %in% c("fitnew"),],aes(x=value))  + geom_density(fill="black")  + theme_bw() 
```

##Generate network

```{r}
posterior<-chains$Species$Predicted %>% filter(parameter %in% c("alpha")) %>% select(-par) %>% mutate(jBird=as.numeric(jBird),jPlant=as.numeric(jPlant)) %>% spread(parameter,value) %>% inner_join(jagsIndexBird) %>% inner_join(jagsIndexPlants)

genLink<-function(alpha){
  p<-inv.logit(alpha)
  state<-rbinom(1,1,p)
}
genNetwork<-function(posterior){
m<-matrix(nrow=length(unique(Ynew_dat$Hummingbird)),ncol=length(unique(Ynew_dat$Iplant_Double)))
colnames(m)<-unique(Ynew_dat$Iplant_Double)
rownames(m)<-unique(Ynew_dat$Hummingbird)

for(bird in unique(Ynew_dat$Hummingbird)){
for(plant in unique(Ynew_dat$Iplant_Double)){
  samp<-posterior %>% filter(Hummingbird %in% bird,Iplant_Double %in% plant) %>% sample_n(1)
  m[bird,plant]<-genLink(alpha=samp$alpha)
}
}

nstat<-networklevel(m,index=c("connectance","niche overlap"),level="lower")
return(nstat)
}

networks$Species$Predicted<-melt(t(sapply(1:20,function(k) genNetwork(posterior = posterior)))) 
```

## Estimated

```{r}
#Run Model
models$Species$Estimated<-runModel(Yobs_dat=Ynew_dat,Ynew_dat=Ynew_dat)

#Get Chains
chains$Species$Estimated<-data.frame(getChains(models$Species$Estimated))
```

### Network

```{r}
posterior<-chains$Species$Estimated %>% filter(parameter %in% c("alpha")) %>% select(-par) %>% mutate(jBird=as.numeric(jBird),jPlant=as.numeric(jPlant)) %>% spread(parameter,value) %>% inner_join(jagsIndexBird) %>% inner_join(jagsIndexPlants)

networks$Species$Estimated<-melt(t(sapply(1:20,function(k) genNetwork(posterior=posterior)))) 
```

## Trait-matching

For hummingbird species i feeding on plant species j observed at time k and sampling event observed by transect 

Observation Model:

$$ Yobs_{i,j,k,d} \sim Binomial(N_{i,j,k},\omega) $$

Process Model:

$$ N_{i,j,k} \sim Binomial(\lambda_{i,j,k}) $$
$$ logit(\lambda_{i,j,k}) = \alpha_i + \beta_{1,i} * Traitmatch_{i,j} $$

```{r}
#Source model
source("models/TraitMatch.R")

#print model
writeLines(readLines("models/TraitMatch.R"))

runModel<-function(Yobs_dat,Ynew_dat,jTraitmatch){
  
  #Inits
  InitStage <- function(){
    #A blank Y matrix - all present
    initY<-rep(1,Dat$Nobs)
    initB<-rep(0.5,Dat$Birds)
    Ynew_pred<-rep(1,Dat$Nnewdata)
    z<-rep(1,Dat$Nobs)
    znew<-rep(1,Dat$Nnewdata)
    
    list(dcam=initB,znew=znew,z=z,Ynew_pred=Ynew_pred)}
  
  #Parameters to track
  ParsStage <- c("alpha","beta1","alpha_mu","alpha_sigma","beta1_sigma","beta1_mu","detect","Ynew_pred","fit","fitnew")
  
  #Jags Data
  Yobs<-(Yobs_dat$Yobs > 0)*1
  Ynew<-(Ynew_dat$Yobs> 0)*1
  
  Dat<-list(
    Yobs=Yobs,
    Birds=max(Yobs_dat$jBird),
    Bird=Yobs_dat$jBird,
    Plant=Yobs_dat$jPlant,
    Nobs=length(Yobs),
    NewBird=Ynew_dat$jBird,
    NewPlant=Ynew_dat$jPlant,
    Ynew=Ynew,
    Nnewdata=length(Ynew),
    Traitmatch=jTraitmatch)
  
  #MCMC options
    system.time(
      m2<-jags(data=Dat,parameters.to.save=ParsStage,inits=InitStage,model.file="models/TraitMatch.jags",n.thin=1,n.iter=1000,n.burnin=900,n.chains=2,DIC=F)
    )
    return(m2)
}

#Run Model
models$Traits$Predicted<-runModel(Yobs_dat=Yobs_dat,Ynew_dat=Ynew_dat,jTraitmatch=jTraitmatch)
```

```{r}
getChains<-function(x,Bird="Bird",Plant="Plant"){
  #extract desired info from the models
  #bind chains
  pc_dive<-reshape2::melt(x$BUGSoutput$sims.array)
  colnames(pc_dive)<-c("Draw","chain","par","value")
  
  #extract parameter name
  pc_dive$parameter<-data.frame(str_match(pc_dive$par,"(\\w+)"))[,-1]
  
  #Extract index
  splitpc<-split(pc_dive,pc_dive$parameter)
  
  #single index
  splitpc[c("alpha","beta1","detect","Ynew_pred")]<-lapply(splitpc[c("alpha","beta1","detect","Ynew_pred")],function(x){
    sv<-data.frame(str_match(x$par,"(\\w+)\\[(\\d+)]"))[,3]
    pc<-data.frame(x,Index=sv)
    return(pc)
  }) 
  
  #bind all matrices back together
  pc_dive<-bind_rows(splitpc)
}

#Get Chains
chains$Traits$Predicted<-getChains(models$Traits$Predicted,Bird="jBird",Plant="jPlant")
```

###Assess Convergence

```{r,cache=FALSE,fig.width=13,fig.height=5}
###Chains
ggplot(chains$Traits$Predicted[chains$Traits$Predicted$parameter %in% c("alpha_mu","beta1_mu"),],aes(x=Draw,y=value,col=as.factor(chain))) + geom_line() + facet_wrap(~parameter,scale="free") + theme_bw() + labs(col="Chain") 
```

```{r,fig.height=12}
ggplot(chains$Traits$Predicted[chains$Traits$Predicted$parameter %in% c("detect"),],aes(x=value),alpha=0.2)  + geom_density() + facet_wrap(~Index,scale="free",ncol=3) + theme_bw()  + ggtitle("Species Level")
```

```{r,fig.height=5,fig.width=11}
ggplot(chains$Traits$Predicted[chains$Traits$Predicted$par %in% c("beta1_mu","beta1_sigma","alpha_mu","alpha_sigma"),],aes(x=Draw,y=value,col=as.factor(chain))) + geom_line() + theme_bw() + labs(col="Chain") + ggtitle("Group Level Parameters") + facet_wrap(~par,scales="free")
```

##Generate network

```{r}
posterior<-chains$Traits$Predicted %>% filter(parameter %in% c("alpha","beta1")) %>% select(-par,jBird=Index) %>% spread(parameter,value) %>% merge(jagsIndexBird) 

genLink<-function(alpha,beta,x){
  p<-inv.logit(alpha + beta * x)
  state<-rbinom(1,1,p)
}
genNetwork<-function(posterior){
m<-matrix(nrow=length(unique(Ynew_dat$Hummingbird)),ncol=length(unique(Ynew_dat$Iplant_Double)))
colnames(m)<-unique(Ynew_dat$Iplant_Double)
rownames(m)<-unique(Ynew_dat$Hummingbird)

for(bird in unique(Ynew_dat$Hummingbird)){
  for(plant in unique(Ynew_dat$Iplant_Double)){
  traitdiff<-traitmatchT[bird,plant]
  samp<-posterior %>% filter(Hummingbird %in% bird) %>% sample_n(1)
  m[bird,plant]<-genLink(alpha=samp$alpha,beta=samp$beta,traitdiff)
}
}

nstat<-networklevel(m,index=c("connectance","niche overlap"),level="lower")
return(nstat)
}

networks$Traits$Predicted<-melt(t(sapply(1:20,function(k) genNetwork(posterior=posterior)))) 
```

###Estimated Data

```{r}
#Run Model
models$Traits$Estimated<-runModel(Yobs_dat=Ynew_dat,Ynew_dat=Ynew_dat,jTraitmatch=jTraitmatch)

#Get Chains
chains$Traits$Estimated<-data.frame(getChains(models$Traits$Estimated),jinterval=intervals[x])
```

```{r}
posterior<-chains$Traits$Estimated %>% filter(parameter %in% c("alpha","beta1")) %>% select(-par,jBird=Index) %>% spread(parameter,value) %>% merge(jagsIndexBird) 

networks$Traits$Estimated<-melt(t(sapply(1:20,function(k) genNetwork(posterior=posterior)))) 
```

# Model Comparison

```{r}
#A bit ugly, but let's assign names.
for(x in 1:length(chains)){
  for(y in 1:length(chains[[x]])){
    chains[[x]][[y]]<-chains[[x]][[y]] %>% mutate(Model=names(chains)[x],Data=names(chains[[x]])[y])
  }
}

allchains<-bind_rows(lapply(chains,bind_rows))

ggplot(allchains[allchains$parameter %in% c("fitnew"),],aes(x=1-value)) + geom_density(aes(fill=Model),alpha=0.5) + theme_bw() + labs(x="Proportion of correctly predicted observations") + scale_x_continuous(labels=scales::percent) + facet_wrap(~Data)
#ggsave("Figures/PredLinksBoth.svg")
#ggsave("Figures/PredLinksBoth.jpeg",height=3,width=7)
```

```{r}
for(x in 1:length(networks)){
  for(y in 1:length(networks[[x]])){
    networks[[x]][[y]]<-networks[[x]][[y]] %>% mutate(Model=names(networks)[x],Data=names(networks[[x]])[y])
  }
}

allnetworks<-bind_rows(lapply(networks,bind_rows))
colnames(allnetworks)<-c("Iteration","Metric","value","Model","Data")
ggplot(allnetworks,aes(x=value)) + geom_density(aes(fill=Model)) + facet_grid(Data~Metric)
```

```{r}
#predicted<-data.frame(getPredictions(mod,Ynew_dat=Ynew_dat),jinterval=intervals[[1]])
```

```{r}
#save.image("ObservedModel.RData")
```