---
title: "Predictive models of species interactions"
output:
html_document:
  toc: true
  number_sections: true
  theme: spacelab
  keep_md: true
editor_options: 
chunk_output_type: console
---

```{r,warning=FALSE,message=FALSE,echo=FALSE,cache=FALSE}
library(chron)
library(dplyr)
library(ggplot2)
library(reshape2)
library(knitr)
library(R2jags)
library(stringr)
library(gridExtra)
library(boot)
library(foreach)
library(bipartite)
library(tidyr)
library(doSNOW)
library(betalink)
library(ggbiplot)
library(igraph)

opts_chunk$set(message=FALSE,warning=FALSE,fig.width=10,fig.height=6,echo=F,cache=F,fig.align='center',fig.path="figureObserved/")

#source functions
source("models/Functions.R")

newModel<-T
```

```{r,echo=F,cache=FALSE}
paste("Run Completed at",Sys.time())
```

```{r}
#reload if needed
#load("ObservedModel.RData")
```

```{r}
fulldat<-read.csv("data/fulldat.csv",row.names=1)
fulldat$timestamp<-as.POSIXct(fulldat$timestamp)

#Testing
fulldat<-fulldat %>% sample_n(100)
```

```{r}
#read in flower morphology data, comes from Nectar.R
fl.morph<-read.csv("data/FlowerMorphology.csv")
missing<-fulldat %>% anti_join(fl.morph)

#remove 
fulldat<-fulldat %>% filter(!Iplant_Double %in% missing$Iplant_Double)

#TraitMatching Matrix
#Bring in Hummingbird Morphology Dataset, comes from
hum.morph<-read.csv("data/HummingbirdMorphology.csv")

#taxonomy change, we are calling them Crowned Woodnymph's now.
hum.morph$English<-as.character(hum.morph$English)
hum.morph$English[hum.morph$English %in% "Green-crowned Woodnymph"]<-"Crowned Woodnymph"

traitmatch<-abs(t(sapply(hum.morph$Bill,function(x){x-fl.morph$Corolla})))
rownames(traitmatch)<-hum.morph$English
colnames(traitmatch)<-fl.morph$Iplant_Double

traitmatch<-round(traitmatch[rownames(traitmatch) %in% fulldat$Hummingbird,colnames(traitmatch) %in% fulldat$Iplant_Double],2)
traitmatch<-traitmatch[sort(rownames(traitmatch)),sort(colnames(traitmatch))]

##Elevation ranges for reference
elevH<-read.csv("data/HummingbirdElevation.csv",row.names=1)
colnames(elevH)[5]<-"Elevation"
elevH$Bird<-1:nrow(elevH)

#high elevation or low elevation
elevP<-read.csv("data/PlantElevation.csv",row.names=1)
colnames(elevP)[5]<-"Elevation"
elevP$Plant<-1:nrow(elevP)
elevP$Iplant_Double<-as.character(elevP$Iplant_Double)

#Merge to observed data
#plants
dathp<-merge(fulldat,elevP,by="Iplant_Double")

#birds
datph<-merge(fulldat,elevH,by="Hummingbird")
```

```{r}
### Define Time Events

#sort by timestamp
datph<-datph[order(datph$timestamp),]

dotime<-function(d){
  d$Timediff<-NA
  if(nrow(d)>1){
    for (x in 2:nrow(d)){
    d$Timediff[x]<-difftime(d$timestamp[x],d$timestamp[x-1],units="mins")  
  }
}
  return(d)
}

datph<-datph %>% group_by(ID,DateP,Hummingbird) %>% do(dotime(.))

#eliminate interaction by the same species within five minutes
datph<-datph[!1:nrow(datph) %in% which(datph$Timediff<5),]
#Day level
#add day ID
sdat<-split(datph,list(datph$ID),drop = T)

sdat<-lapply(sdat,function(x){
  x<-droplevels(x)
  x$Day<-as.numeric(as.factor(x$DateP))
  return(x)
})

indatraw<-bind_rows(sdat)
```

```{r}
#match the traits
traitmelt<-melt(traitmatch)
colnames(traitmelt)<-c("Hummingbird","Iplant_Double","Traitmatch")

#dummy presence variable
indatraw$Yobs<-1
```

```{r,fig.height=4,fig.width=8}
##Summarize daily interactions
datday<-indatraw %>%filter(!is.na(ele)) %>% mutate(interval=cut(timestamp,4)) %>% dplyr::group_by(Hummingbird,Iplant_Double,ID,Day,interval) %>% dplyr::summarize(Yobs=sum(Yobs),ele=mean(ele,na.rm=T),Date=min(format(timestamp,"%m/%d/%Y")))  %>% mutate(Yobs=(Yobs>0)*1) %>% mutate(site=factor(ele>1700)) %>% arrange(Date)

levels(datday$site)<-c("Maquipucuna","Santa Lucia")

rect <- data.frame(xmin=min(as.POSIXct(datday$Date,format="%m/%d/%Y")), xmax=sort(as.POSIXct(unique(datday$interval)))[4], ymin=-Inf, ymax=Inf)

timeplot<-datday %>% group_by(Date) %>% dplyr::summarize(n=sum(Yobs))

ggplot(timeplot,aes(x=strptime(Date,"%m/%d/%Y"),y=as.integer(n))) + geom_line() + geom_rect(data=rect, aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax), fill="red",alpha=0.2,inherit.aes = FALSE) + theme_bw() + scale_x_datetime() + labs(x="Date",y="Observed Interactions") + scale_y_continuous(breaks=scales::pretty_breaks())
```

```{r}
#Assign site
#Species list at each site
species_list<-datday %>% group_by(site) %>% distinct(Hummingbird)
```

#Absence data

```{r}
#For each observation, fill matrix with other species at the site

fill_species<-function(x){
  original<-x
  to_fill<-species_list$Hummingbird[!species_list$Hummingbird %in% x$Hummingbird]

  to_return<-list()
  for(s in 1:length(to_fill)){
    x$Hummingbird<-to_fill[s]
    x$Yobs<-0
    to_return[[s]]<-x
  }
  return(bind_rows(original,to_return))
}

indat<-datday %>% ungroup() %>% mutate(Index=1:nrow(.)) %>% group_by(Index) %>% do(fill_species(.)) %>% select(-Index)
```

#Models

```{r}
models<-list()
chains<-list()
networks<-list()
```

```{r}
indat$jinterval<-as.numeric(indat$interval)

#Easiest to work with jags as numeric ordinal values
indat$Hummingbird<-as.factor(indat$Hummingbird)
indat$Iplant_Double<-as.factor(indat$Iplant_Double)
indat$jBird<-as.numeric(indat$Hummingbird)
indat$jPlant<-as.numeric(indat$Iplant_Double)
indat$jinterval<-as.numeric(indat$interval)

jagsIndexBird<-data.frame(Hummingbird=levels(indat$Hummingbird),jBird=1:length(levels(indat$Hummingbird)))

jagsIndexPlants<-data.frame(Iplant_Double=levels(indat$Iplant_Double),jPlant=1:length(levels(indat$Iplant_Double)))

#Similiarly, the trait matrix needs to reflect this indexing.
jTraitmatch<-traitmatch[rownames(traitmatch) %in% unique(indat$Hummingbird),colnames(traitmatch) %in% unique(indat$Iplant_Double)]

indat$Index<-1:nrow(indat)
indat<-droplevels(indat)

#Turn Time and ID into numeric indexes
indat$jTime<-as.numeric(as.factor(indat$Date))
indat$jID<-as.numeric(as.factor(indat$ID))

indat$Month<-months(indat$Date)
indat$Season[indat$Month %in% c("Jun","Jul","Aug","Sep","Oct")]<-"Dry"
indat$Season[!indat$Month %in% c("Jun","Jul","Aug","Sep","Oct")]<-"Wet"

indat$jSeason<-as.numeric(as.factor(indat$Season))
timeplot<-indat %>% group_by(Date,Season) %>% dplyr::summarize(n=sum(Yobs))

ggplot(timeplot,aes(x=strptime(Date,"%m/%d/%Y"),y=as.integer(n))) + geom_line(size=0.2) + geom_point(aes(col=Season)) + geom_rect(data=rect, aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax), fill="red",alpha=0.2,inherit.aes = FALSE) + theme_bw() + scale_x_datetime() + labs(x="Date",y="Observed Interactions") + scale_y_continuous(breaks=scales::pretty_breaks()) + scale_color_manual(values=c("grey60","black"))

#Split data
split_dat<-split(indat,indat$interval)
Yobs_dat<-bind_rows(split_dat[1:3])
Ynew_dat<-split_dat[[4]]
```


```{r}
#Source model
source("models/Traitmatching_Detect_Elevation_Beta.R")

#print model
writeLines(readLines("models/Traitmatching_Detect_Elevation_Beta.R"))

#Run Model
runModel<-function(Yobs_dat,Ynew_dat){
  
  #Inits
  InitStage <- function(){

    #A blank Y matrix - all present
    initY<-rep(1,Dat$Nobs)
    initB<-rep(0.5,Dat$Birds)
    Ynew_pred<-rep(1,Dat$Nnewdata)
    z<-rep(1,Dat$Nobs)
    znew<-rep(1,Dat$Nnewdata)
    occ<-array(dim=c(Dat$Birds,Dat$Plants,Dat$Cameras),data=1)
    
    list(dcam=initB,znew=znew,z=z,Ynew_pred=Ynew_pred,occ=occ)}
  
  #Parameters to track
  ParsStage <- c("Ynew_pred","Enew","alpha_occ","beta_occ","beta2_occ","detect","alpha","beta_season","beta_int","beta_trait")
  
  #Jags Data
  Yobs<-Yobs_dat$Yobs
  Ynew<-Ynew_dat$Yobs
  
  Dat<-list(
    Yobs=Yobs,
    Birds=max(c(Yobs_dat$jBird,Ynew_dat$jBird)),
    Season=indat %>% ungroup() %>% select(jID,jSeason) %>% arrange(jID) %>% distinct(jID,jSeason) %>% .$jSeason,
    Traitmatch=jTraitmatch,
    elevation=indat %>% ungroup() %>% select(jID,ele) %>% arrange(jID) %>% distinct(jID,ele) %>% .$ele,
    Bird=Yobs_dat$jBird,
    Plant=Yobs_dat$jPlant,
    Plants=max(c(Yobs_dat$jPlant,Ynew_dat$jPlant)),
    Cameras=max(c(Yobs_dat$jID,Ynew_dat$jID)),
    Camera=Yobs_dat$jID,
    NewCamera=Ynew_dat$jID,
    Nobs=length(Yobs),
    NewBird=Ynew_dat$jBird,
    NewPlant=Ynew_dat$jPlant,
    Ynew=Ynew,
    Nnewdata=length(Ynew))
  
  #MCMC options
    mtime<-system.time(
      m2<-jags(data=Dat,parameters.to.save=ParsStage,inits=InitStage,model.file="models/Traitmatching_Detect_Elevation_Beta.jags",n.thin=2,n.iter=30000,n.burnin=29600,n.chains=2,DIC=F)
    )
    print(mtime)
    return(m2)
}

models$Trait_Detect_Elevation_Beta<-runModel(Yobs_dat=Yobs_dat,Ynew_dat=Ynew_dat)
```

```{r}
#Get Chains
getChains<-function(mod){
  
  pc<-reshape2::melt(mod$BUGSoutput$sims.array)
  colnames(pc)<-c("Draw","chain","par","value")
  
  #extract parameter name
  pc$parameter<-data.frame(str_match(pc$par,"(\\w+)"))[,-1]
  
  #Extract index
  splitpc<-split(pc,pc$parameter)
  
    splitpc[c("alpha_occ","beta_occ","beta2_occ","detect")]<-lapply(
    splitpc[c("alpha_occ","beta_occ","beta2_occ","detect")],function(x){
      sv<-data.frame(str_match(x$par,"(\\w+)\\[(\\d+)]"))[,3]
      pc<-data.frame(x,jBird=sv)
    })
    
      splitpc[c("beta_season","alpha","beta_trait","beta_int")]<-lapply(
  splitpc[c("beta_season","alpha","beta_trait","beta_int")],function(x){
    print(head(x))
    sv<-data.frame(str_match(x$par,"(\\w+)\\[(\\d+)]"))[,3]
    pc<-data.frame(x,jBird=sv)
  })
  
  splitpc[c("Ynew_pred","Enew")]<-lapply(
    splitpc[c("Ynew_pred","Enew")],function(x){
    sv<-data.frame(str_match(x$par,"(\\w+)\\[(\\d+)]"))[,3]
    pc<-data.frame(x,Index=sv)
    })
    
  chains<-bind_rows(splitpc)
return(chains)}
```

```{r}
##Generate chains
chains$Trait_Detect_Elevation_Beta<-getChains(models$Trait_Detect_Elevation_Beta)

##Generate networks
networks$Trait_Detect_Elevation_Beta<-getPredictions(chains$Trait_Detect_Elevation_Beta,Ynew_dat = Ynew_dat)
```

###Assess Convergence

```{r,cache=FALSE,fig.width=5,fig.height=2}
###Chains
chains$Trait_Detect_Elevation_Beta %>% filter(parameter == "beta_int") %>% ggplot(.,aes(x=Draw,y=value,col=as.factor(chain))) + geom_line()  + theme_bw() + labs(col="Chain") + facet_wrap(~jBird)
```

### Effect of season on trait-matching

```{r}
beta_int<-chains$Trait_Detect_Elevation_Beta %>% filter(parameter %in% "beta_int") %>% group_by(jBird) %>% dplyr::summarize(mean=mean(value),lower=quantile(value,0.05),upper=quantile(value,0.95))

#Which contain 0 effect
to_color<-beta_int %>% group_by(jBird) %>% dplyr::summarize(sig=!(upper > 0 & lower < 0))

#Grab sig ones
beta_int<-beta_int %>% inner_join(to_color)  %>% mutate(jBird=as.numeric(as.character(jBird))) %>% inner_join(jagsIndexBird) %>% arrange(mean)

#reorder
beta_int$Hummingbird<-factor(beta_int$Hummingbird,levels=beta_int$Hummingbird)

ggplot(beta_int,aes(x=Hummingbird)) + geom_pointrange(aes(y=mean,ymin=lower,ymax=upper,col=sig),size=1) + coord_flip() + labs(col="Effect of Season on Trait-matching") + theme(legend.position = "bottom") + theme_bw() + scale_color_manual(values=c("grey60","black"))
```

```{r}
#Assign names.
for(x in 1:length(chains)){
    chains[[x]]<-chains[[x]] %>% mutate(Model=names(chains)[x])
  }

allchains<-bind_rows(lapply(chains,bind_rows))

Ynew_dat$Index<-1:nrow(Ynew_dat)
```

## By Species
```{r,fig.height=7,fig.width=8}
disc<-allchains %>% filter(parameter %in% "Enew") %>% mutate(Index=as.numeric(Index)) %>% inner_join(Ynew_dat,by="Index") %>% group_by(Model,Yobs,Hummingbird) %>% dplyr::summarize(value=mean(value)) %>% filter(!Model %in% "Random")

ggplot(disc,aes(x=Hummingbird,y=value)) + geom_point(size=2)  + labs(x="Species",y="Mean Predictive Error") + coord_flip() + facet_grid(~Yobs,scales="free") + theme_bw()

#stripe<-allchains %>% filter(parameter %in% "Enew") %>% mutate(Index=as.numeric(Index)) %>% inner_join(Ynew_dat,by="Index") %>% filter(Hummingbird %in% "White-whiskered Hermit") %>% group_by(Model,Index,Yobs) %>% dplyr::summarize(value=mean(value))

#ggplot(stripe,aes(x=as.factor(Index),y=value,col=Model)) + geom_point()  + labs(y="Mean Predictive Error") + coord_flip() + facet_wrap(~Yobs,scales="free")
```

## Detectability

```{r}
allchains %>% filter(parameter %in% "detect") %>% mutate(jBird=as.numeric(jBird)) %>% inner_join(jagsIndexBird) %>% ggplot(.,aes(x=value)) + geom_density(fill="black") + facet_wrap(~Hummingbird,scales="free") + theme_bw() + scale_fill_manual(values=c("grey60","black"))
```

## Proportion of predicted links

```{r}
m_new<-acast(Ynew_dat,Hummingbird~Iplant_Double,value.var="Yobs",fun.aggregate = sum)
m_new<-(m_new > 0) * 1

#Network statistics
obs_net<-networklevel(m_new,index=c("connectance","niche overlap"),level="lower")
obs_net<-melt(data.frame(Metric=names(obs_net),value=obs_net))

#Also grab a melted version to match posterior format
obs_matrix<-melt(m_new) %>% select(Hummingbird=Var1,Iplant_Double=Var2,value) %>% mutate(Link=paste(Hummingbird,Iplant_Double,sep="_"))
```

```{r,fig.height=4,fig.width=7}
netdf<-melt(networks)

netdf %>% group_by(L1,value) %>% dplyr::summarize(n=n()) %>% spread(value,n) %>% select(Model=L1,Presence=`1`,Absence=`0`) %>% mutate(p=Presence/(Presence + Absence)*100)

paste("True presence rate is:",round(sum(obs_matrix$value==1)/(sum(obs_matrix$value==1)+sum(obs_matrix$value==0)),3)*100)
```

```{r,fig.height=4,fig.width=7}
true_positives<-netdf %>% select(Hummingbird=Var1,Iplant_Double=Var2,value,Iteration=L2,Model=L1) %>% mutate(Link=paste(Hummingbird,Iplant_Double,sep="_")) %>% group_by(Model,Link,Iteration) %>% dplyr::summarize(value=max(value)) %>% filter(value==1) %>% filter(Link %in% obs_matrix$Link[obs_matrix$value==1]) %>% group_by(Model,Iteration) %>% dplyr::summarize(n=n()) %>% dplyr::summarize(mean=mean(n),lower=quantile(n,0.05),upper=quantile(n,0.95))

true_negatives<-netdf %>% select(Hummingbird=Var1,Iplant_Double=Var2,value,Iteration=L2,Model=L1) %>% mutate(Link=paste(Hummingbird,Iplant_Double,sep="_")) %>% group_by(Model,Link,Iteration) %>% dplyr::summarize(value=max(value)) %>% filter(value==0) %>% filter(Link %in% obs_matrix$Link[obs_matrix$value==0]) %>% group_by(Model,Iteration) %>% dplyr::summarize(n=n()) %>% dplyr::summarize(mean=mean(n),lower=quantile(n,0.05),upper=quantile(n,0.95))

false_positives<-netdf %>% select(Hummingbird=Var1,Iplant_Double=Var2,value,Iteration=L2,Model=L1) %>% mutate(Link=paste(Hummingbird,Iplant_Double,sep="_")) %>% group_by(Model,Link,Iteration) %>% dplyr::summarize(value=max(value)) %>% filter(value==1) %>% filter(Link %in% obs_matrix$Link[obs_matrix$value==0]) %>% group_by(Model,Iteration) %>% dplyr::summarize(n=n()) %>% dplyr::summarize(mean=mean(n),lower=quantile(n,0.05),upper=quantile(n,0.95))

false_negatives<-netdf %>% select(Hummingbird=Var1,Iplant_Double=Var2,value,Iteration=L2,Model=L1) %>% mutate(Link=paste(Hummingbird,Iplant_Double,sep="_")) %>% group_by(Model,Link,Iteration) %>% dplyr::summarize(value=max(value)) %>% filter(value==0) %>% filter(Link %in% obs_matrix$Link[obs_matrix$value==1]) %>% group_by(Model,Iteration) %>% dplyr::summarize(n=n()) %>% dplyr::summarize(mean=mean(n),lower=quantile(n,0.05),upper=quantile(n,0.95))

conf_matrix<-melt(list(true_positives=true_positives,true_negatives=true_negatives,false_positives=false_positives,false_negatives=false_negatives)) %>% select(Model,variable,value,Metric=L1) %>% spread(Metric,value) %>% mutate(accuracy=(true_positives+true_negatives)/(true_positives+true_negatives+false_positives+false_negatives),recall=true_positives/(true_positives+false_negatives),precision=true_positives/(true_positives+false_positives)) %>% select(Model,stat=variable,recall,precision,accuracy) %>% melt(id.vars=c("Model","stat")) %>% dcast(Model+variable~stat)

ggplot(conf_matrix,aes(x=Model)) + facet_grid(~variable,scales="free") + geom_linerange(aes(ymin=lower,ymax=upper)) + geom_point(aes(y=mean)) + coord_flip() + theme_bw() + labs(y="value")
```

## Predicted network statistics

Dashed line is the observed network from the time-series.

```{r,fig.height=7,fig.width=10}

#Get network statistics for all models.
allnetworks<-lapply(networks,function(x){
    lapply(x,function(y){
      d<-networklevel(y,index=c("connectance","niche overlap"),level="lower")
      return(data.frame(Metric=names(d),value=d))
    })
  })
allnetworks<-melt(allnetworks,id.var=c("Metric","value"))

#Plot
allnetworks<-allnetworks %>% select(Model=L1,Metric,value) %>% mutate(Level=str_extract(Model,"_(\\w+)"))%>% separate(Model,sep="_",c("Model","Detect","Elevation")) %>% select(-Detect,-Elevation) 

allnetworks$Level[is.na(allnetworks$Level)]<-""
allnetworks$Level<-as.factor(allnetworks$Level)
levels(allnetworks$Level)<-c("","+Detect","+Detect +Elevation")

ggplot(allnetworks,aes(x=value)) + geom_density(aes(fill=Model),alpha=0.5) + facet_grid(Level~Metric) + geom_vline(data=obs_net,aes(xintercept=value),linetype="dashed") + theme_bw()
```

Dissimilairty in interactions (Beta_WN from Poisot 2012)
Dashed line is the observed network from the time-series.

Note that this is really a measure of dissimilairty in one level (hummimngbirds), as the dissimilarity in plants is fixed by the sampling protocol. While there be a correlation between the species pool and the chosen plant to film, this is filtered by a human placing a camera at that plant, and as such isn't a true measure of plant dissimiality.

```{r}
#Observed dissimilarity by season.
dry_new<-acast(Ynew_dat %>% filter(Season=="Dry"),Hummingbird~Iplant_Double,value.var="Yobs",fun.aggregate = sum)
wet_new<-acast(Ynew_dat %>% filter(Season=="Wet"),Hummingbird~Iplant_Double,value.var="Yobs",fun.aggregate = sum)

#Turn into binary links
dry_new<-dry_new > 0 * 1
wet_new<-wet_new > 0 * 1

obs_dis<-melt(betalink(graph.incidence(dry_new),graph.incidence(wet_new)))
colnames(obs_dis)<-c("value","Betadiversity")

```

```{r,fig.height=7,fig.width=9}

pred_beta<-function(dat,Ynew_dat){
  Ynew_pred<-Ynew_dat %>% dplyr::select(-jinterval,-interval) %>% mutate(Index=1:nrow(Ynew_dat)) %>% inner_join(dat,by="Index")
  
#Wet Season
wet_pred<-acast(Ynew_pred %>% filter(Season=="Wet"),Hummingbird~Iplant_Double,value.var="value",fun.aggregate = sum)

#Dry Season
dry_pred<-acast(Ynew_pred %>% filter(Season=="Dry"),Hummingbird~Iplant_Double,value.var="value",fun.aggregate = sum)

#Turn into binary links
dry_pred<-dry_pred > 0 * 1
wet_pred<-wet_pred > 0 * 1

obs_dis<-melt(betalink(graph.incidence(dry_pred),graph.incidence(wet_pred)))
return(obs_dis)
}

betastat<-chains$Trait_Detect_Elevation_Beta %>% filter(parameter=="Ynew_pred") %>% mutate(Index=as.numeric(as.character(Index))) %>% group_by(Draw,chain) %>% do(pred_beta(.,Ynew_dat))
colnames(betastat)<-c("Draw","chain","value","Betadiversity")

#recode levels to make more attractive.
betastat$Betadiversity<-factor(betastat$Betadiversity)
levels(betastat$Betadiversity)[levels(betastat$Betadiversity) %in% "WN"]<-"Interaction Dissimilarity"
levels(betastat$Betadiversity)[levels(betastat$Betadiversity) %in% "ST"]<-"Interaction Turnover"
levels(betastat$Betadiversity)[levels(betastat$Betadiversity) %in% "OS"]<-"Interaction Rewiring"
levels(betastat$Betadiversity)[levels(betastat$Betadiversity) %in% "S"]<-"Species Turnover"

obs_dis$Betadiversity<-factor(obs_dis$Betadiversity)
levels(obs_dis$Betadiversity)[levels(obs_dis$Betadiversity) %in% "WN"]<-"Interaction Dissimilarity"
levels(obs_dis$Betadiversity)[levels(obs_dis$Betadiversity) %in% "ST"]<-"Interaction Turnover"
levels(obs_dis$Betadiversity)[levels(obs_dis$Betadiversity) %in% "OS"]<-"Interaction Rewiring"
levels(obs_dis$Betadiversity)[levels(obs_dis$Betadiversity) %in% "S"]<-"Species Turnover"

ggplot(betastat %>% filter(!Betadiversity %in% "Species Turnover"),aes(x=value)) + geom_density(alpha=0.4,fill="black") + facet_wrap(~Betadiversity,scales="free") + geom_vline(data=obs_dis  %>% filter(!Betadiversity %in% "Species Turnover"),aes(xintercept=value),linetype="dashed") + theme_bw()
```

```{r}
save.image("TraitmatchingModel.RData")
```